{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
fixed definition of jun
use \cite for Barthe06

\begin{definition}{jun}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. It is defined
on all junction points $[c]^n$ in the source program and its domain looks like $max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

@@

To make this distinction a new type system is introduced. Type judgments have the form
$\vdash_\alpha [c]_{\alpha'}^n : E$, where $E$ is a function that maps labels to security
levels.\footnote{Given $E$ it is easy to define a security environment $se$. For a definition
of $E$ see Barthe et. al. 2006} $\alpha$ denotes if $c$ is \textit{part of} a branching
instruction that branches on secret ($\bullet$) or public ($\circ$) data and $\alpha'$ is the
security level of the guard \textit{in} the branching instruction.

>>>>

\begin{definition}{jun}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. It is defined
on all junction points $[c]^n$ in the source program and its domain is $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

@@

To make this distinction a new type system is introduced. Type judgments have the form
$\vdash_\alpha [c]_{\alpha'}^n : E$, where $E$ is a function that maps labels to security
levels.\footnote{Given $E$ it is easy to define a security environment $se$. For a definition
of $E$ see \cite{Barthe06}.} $\alpha$ denotes if $c$ is \textit{part of} a branching
instruction that branches on secret ($\bullet$) or public ($\circ$) data and $\alpha'$ is the
security level of the guard \textit{in} the branching instruction.
